
  \font\bigbigbf = cmb10 scaled \magstep 2
  \font\bigbf = cmb10 scaled \magstep 1
  \nopagenumbers
  \overfullrule = 0 pt
  
  \headline={\ifnum\pageno=1\else{\rm\hfill Mark Wagner, Page \folio\voffset=2\normalbaselineskip}\fi}
  \centerline{\bigbigbf Mark Wagner}
  \medskip

  \centerline{(206) 354-9071}

  \centerline{mark@lanfear.net}

  \bigskip

  {\parindent = 0pt \bigbigbf Objective}
  \medskip
  {\parindent = 0pt
  To obtain position that builds and maintains valuable and
  robust computing environments through automation, repeatable
  processes, and insightful monitoring.
  }
  \bigskip

  {\parindent = 0pt \bigbigbf Skills}
  \medskip
  
  \item{$\bullet$} Operations: Deep experience managing Linux systems and critical infrastructure services. Full life-cycle automation. Resolution of issues in complex distributed systems including self-managed data centers and cloud environments.
  \item{$\bullet$} Software Development: Experienced python and ruby developer. Can analyze and debug applications written in many other languages including C, JavaScript, PHP, and Perl. Efficient development with continuous testing, integration, and deployment tools. Theoretical knowledge of software design principles and computer science topics.
  \item{$\bullet$} Security: Secured Internet-facing systems. Achieved ISO 27001, PCI DSS, and HIPPA compliance for computing systems.
  \bigskip

  {\parindent = 0pt \bigbigbf Employment}
  \medskip
  
  \line{{\bigbf Senior Site Reliability Engineer} \hfil February 2018 to the present}
  {\parindent = 0pt Skytap, Inc.}
  
  \item{$\bullet$} Approved production changes. Mentored junior engineers.
  \item{$\bullet$} Managed git source code repositories hosted with GitHub and locally with Gerrit.
  \item{$\bullet$} Supported Kubernetes container orchestration system with Docker as the container implementation.
  \item{$\bullet$} Managed DNS, DHCP, LDAP, NTP, SMTP, and certificate authority infrastructure services.
  \item{$\bullet$} Supported observabity monitoring systems: Zabbix, ELK (Elasticsearch, Logstash, and Kibana) stack and TIG (Telegraf, InfluxDB, Grafana) stack.
  \item{$\bullet$} Served as a MySQL DBA: provided operational support, analyzed performance, and planned capacity.
  \item{$\bullet$} Participated in open source projects: filed bug reports, suggested fixes, and helped others.
    \medskip
  
  \line{{\bigbf Senior Operations Engineer} \hfil November 2013 to February 2018}
  {\parindent = 0pt Skytap, Inc.}
  
  \item{$\bullet$} Supported Skytap's global cloud hosting platform based on VMware ESXi, Linux, Solaris, HP hardware, and 3PAR block storage.
  \item{$\bullet$} Improved hardware provisioning speed by creating installation checklists and writing scripts to automate device testing and configuration.
  \item{$\bullet$} Automated system deployment and configuration with Foreman, Puppet, and Ansible.
  \item{$\bullet$} Configured and maintained network infrastructure such as IPSEC VPNs, F5 BigIP load balancers, Juniper routers, and Cisco Nexus switches.
    \medskip
  
  \line{{\bigbf Senior System Administrator} \hfil February 2013 to November 2013}
  {\parindent = 0pt Point Inside, Inc.}
  
  \item{$\bullet$} Managed AWS resources (EC2, VPC, RDS, SQS, SNS, CloudWatch) with command line tools and custom Ruby scripts using the AWS SDK.
  \item{$\bullet$} Designed and implemented scalable architecture with AWS Auto Scaling.
  \item{$\bullet$} Maintained infrastructure with chef. Wrote custom chef cookbooks.
  \item{$\bullet$} Wrote release automation scripts.
  \item{$\bullet$} Diagnosed and helped resolve HAProxy, Apache, Tomcat, and Solr issues at the network, server, and application levels.
  \item{$\bullet$} Mentored and trained junior system administrators.
  \item{$\bullet$} Researched new AWS services and other cloud technologies.
    \medskip
  
  \line{{\bigbf Senior System Administrator} \hfil July 2010 to February 2013}
  {\parindent = 0pt Intelius, Inc.}
  
  \item{$\bullet$} Identified and resolved system faults and performance problems by debugging PHP code, running Apache under a debugger, examining MySQL statistics, and analyzing OS and kernel metrics.
  \item{$\bullet$} Analyzed, documented, and remediated PCI compliance issues.
  \item{$\bullet$} Evaluated hybrid cloud systems and implemented the OpenNebula / KVM platform.
  \item{$\bullet$} Installed and administered a Hadoop cluster.
  \item{$\bullet$} Handled custom compilation and deployment of Apache, PHP, and other software packages.
  \item{$\bullet$} Maintained configuration of the SEC log analysis system, BIND DNS servers, and cfengine configuration management software.
  \item{$\bullet$} Administered SAN and NAS storage systems.
  \item{$\bullet$} Researched and prototyped new system administration software and methodologies.
  \item{$\bullet$} Served as a backup MySQL DBA. Wrote automated database publishing scripts.
    \medskip
  
  \line{{\bigbf Senior Systems Administrator} \hfil December 2008 to March 2010}
  {\parindent = 0pt Infopia, Inc.}
  
  \item{$\bullet$} System and SAN administrator for servers running Infopia's business-critical ecommerce SaaS system.
  \item{$\bullet$} Planned and implemented data center migration from managed hosting to new servers in a self-hosted environment.
  \item{$\bullet$} Installed and configured infrastructure servers: DNS, mail, LDAP, backup, and monitoring.
    \medskip
  
  \line{{\bigbf Systems Programmer} \hfil October 2001 to December 2008}
  {\parindent = 0pt University of Washington Medical Center}
  
  \item{$\bullet$} Lead development of enterprise-wide Linux standard.
  \item{$\bullet$} Developed automated Linux installation and maintenance process.
  \item{$\bullet$} Trained junior sysadmins.
  \item{$\bullet$} Handled all aspects of system security in an unsecured, Internet-connected environment, including vulnerability analysis, subnet and host-based firewalls, and system hardening.
  \item{$\bullet$} Provided support for computer-controlled medical equipment, including imaging modalities and radiation treatment devices.
  \item{$\bullet$} Provided software installation and support. Compiled software from source. Performed fault analysis using system tools and debuggers.
  \item{$\bullet$} Performed system capacity planning and hardware acquisition.
    \medskip
  
  \line{{\bigbf Internet Systems Developer and Administrator} \hfil October 1998 to October 2001}
  {\parindent = 0pt Horvitz Newspapers Inc}
  
  \item{$\bullet$} Designed and coded automated web site generation and archiving system in Perl.
  \item{$\bullet$} Webmaster duties: Compiled, installed, troubleshot, and performance tuned Apache.
  \item{$\bullet$} Security administrator for web sites and firewalls. Evaluated Internet-related security risks. Set up and maintained Linux-based firewalls.
  \item{$\bullet$} Installed and maintained DNS, ftp, monitoring, and backup servers and Sun and x86 hardware.
    \medskip
  
  \line{{\bigbf Fraud Application Support} \hfil January 1998 to October 1998}
  {\parindent = 0pt AT\&T Wireless Services Inc}
  
  \item{$\bullet$} Provided technical support to customers (Los Angeles Cellular, Cantel).
  \item{$\bullet$} Planned projects and solved problems in a complex environment involving vendor, customer, AT\&T, and VAN systems.
  \item{$\bullet$} Trained support personnel.
  \item{$\bullet$} Participated in CTIA EDI standards writing process.
  \item{$\bullet$} Wrote parts of application support guide.
  \item{$\bullet$} Designed and implemented enhancements to fraud application.
  \item{$\bullet$} Wrote maintenance scripts in Perl and ksh.
    \medskip
  
  \line{{\bigbf Unix System Administrator} \hfil May 1996 to August 1997}
  {\parindent = 0pt Ameritech Communications Inc}
  
  \item{$\bullet$} Administered Sun and HP servers.
  \item{$\bullet$} Installed and tuned Solaris.
  \item{$\bullet$} Installed and upgraded hardware.
  \bigskip

  {\parindent = 0pt \bigbigbf Education}
  \medskip
  
  \line{{\bigbf Master of Science, Computer Science} \hfil March 2003}
  {\parindent = 0pt University of Washington-Seattle}
  
    \medskip

  \line{{\bigbf Computer Science, Philosophy} \hfil August 1992 to May 1996}
  {\parindent = 0pt University of Wisconsin-Madison}
  
    \medskip

  \line{{\bigbf Bachelor of Arts, Philosophy} \hfil June 1992}
  {\parindent = 0pt Lawrence University}
  
    \medskip

  {\parindent = 0pt \bigbf Certifications}
  
  \item{$\bullet$} Certificate in Cloud Computing, University of Washington
  \medskip

  \bigskip

  \bye
